INTELLIGENT SYSTEMS

### 2021-04-02 paper_4.tex
finish 4.3.2

\subsection{THE PROPOSED INTEL-TUT DATA SET}

>>>>

\subsection{THE PROPOSED INTEL-TUT DATA SET}
The purpose of the dataset is to help the algorithms to determine if the color 
constancy value obtained is to be considered good or not. If an algorithm 
does not find a change in this value on the same set of images taken by the 
same camera, then this algorithm is able to have a uniform color constancy 
and consequently would produce optimal outputs.

\subsubsection{Light Sources}
A variety of devices were used that were capable of producing a light source. 
Each property such as luminance (Lux), color temperature (CCT) and CIE 
xy chromaticity, have been appropriately set to have an equitable acquisition.

\subsubsection{Cameras}
Three types of camera are used for the construction of the dataset. Two 
of these belong to the high-end, while a third belongs to the category of 
mobile phones. To achieve correct color correction, several 3x3 size color 
conversion matrices (\emph{CCMs}) were used. In other words, try to transform 
the components of the image from RGB to sRGB in order to adapt them to 
the lighting under which the image is viewed. For the outdoors, 10 CCMs 
were used based on the type of illumination. Another factor that required 
correction was the color shading (\emph{CS}). This only requires correction for the 
images coming from the mobile phone.
